Price of Anarchy for Mean Field Games

### 2018-07-24 PoA.tex
minor edits again

	% lower bound for (b_2 + b2 bar) u_t
	Moreover, we can derive a uniform lower bound for $(b_2 + \bar{b}_2) u_t^{b_2}$ for any large enough $b_2$ by expanding this whole expression with equation (\ref{eq:riccati_ut_sol}). Let $\epsilon_1 > 0$ so that $\epsilon_1 < \min \{ c_{\delta_u^{b_2 \to \infty}}, D^{u,b_2 \to \infty} \}$, for example $\epsilon_1 = \frac{1}{2} \min \{ c_{\delta_u^{b_2 \to \infty}}, D^{u,b_2 \to \infty} \}$. Then there exists $b_2^{*,lower} := b_2^{*,lower}(\epsilon_1) 	>0$ such that for all $b_2 \geq b_2^{*,lower}$,
	$$ 
	\max \left\{  \left\vert \frac{\delta_u^{+,b_2}}{b_2 + \bar{b}_2}  - c_{\delta_u^{b_2 \to \infty}} \right\vert, \   \left\vert \frac{\delta_u^{-,b_2}}{b_2 + \bar{b}_2}  - (-c_{\delta_u^{b_2 \to \infty}}) \right\vert, \vert D^{u,b_2} - D^{u,b_2\to \infty} \vert,  \left\vert \frac{1}{b_2 + \bar{b}_2} \right\vert  \right\} \leq \epsilon_1,
	$$ 
	so that
	\begin{IEEEeqnarray}{rCl}
		(b_2 + \bar{b}_2) u_t^{b_2} &\geq&  (b_2 + \bar{b}_2) \frac{D^{u,b_2} \delta_u^{+, b_2} }{ (\delta_u^{+,b_2} - \delta_u^{-,b_2}) + B^{b_2}D^{u,b_2} } \nonumber \\
		&=& \frac{D^{u,b_2} \frac{\delta_u^{+, b_2}}{b_2+ \bar{b}_2} }{ \frac{1}{b_2 + \bar{b}_2} \cdot \frac{\delta_u^{+,b_2} - \delta_u^{-,b_2}}{b_2 + \bar{b}_2} + \frac{D^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} } \nonumber \\
		&\geq& \frac{(D^{u,b_2 \to \infty} - \epsilon_1 ) \cdot (c_{\delta_u^{b_2 \to \infty}} - \epsilon_1) }{ \epsilon_1 \cdot (2 c_{\delta_u^{b_2 \to \infty}} + 2 \epsilon_1) + (D^{u,b_2 \to \infty} + \epsilon_1) / (r+ \bar{r}(1-\bar{s})^2) } =: m_u(\epsilon_1)
	\label{eq:ut_uniform_lower_bound_b2_infinity}
	\end{IEEEeqnarray}

	% upper bound for u_t, w_t
	Also, from the explicit formula (\ref{eq:riccati_ut_sol}) of $u_t^{b_2}$, given any fixed $b_2$, we can compute the derivative of $u_t^{b_2}$ with respect to time $t$ and obtain:
	\begin{equation*}
		\frac{d u_t^{b_2}}{dt} = \frac{\left(B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} \right) \cdot (\delta_u^{+,b_2} - \delta_u^{-,b_2}) e^{- (\delta_u^{+,b_2} - \delta_u^{-,b_2})(T-t) } }{\left[(- \delta_u^{-,b_2} + B^{b_2} D^{u,b_2} )  + (\delta_u^{+,b_2} - B^{b_2} D^{u,b_2} )e^{- (\delta_u^{+,b_2} - \delta_u^{-,b_2})(T-t)} \right]^2 }.
	\end{equation*}
	Hence, the function $t \mapsto u_t^{b_2}$ is increasing when $B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} > 0$. Since 
	$$ B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} \xrightarrow[b_2 \to \infty]{} \infty,$$
	there must exists $b_2^{*,u,upper}>0$ such that for all $b_2 \geq b_2^{*,u,upper}$, we have $t \mapsto u_t^{b_2}$ being increasing and 
	$$ \sup_{b_2 \geq b_2^{*,u,upper}} \sup_{0\leq t \leq T} \left\{ u_t^{b_2} \right\} \leq \sup_{b_2 \geq b_2^{*,u,upper}} \left\{ u_T^{b_2}\right\}  = \sup_{b_2 \geq b_2^{*,u,upper}} \{ D^{u,b_2}  \} \leq D^{u,b_2 \to \infty} + 1.$$
	Idem for $t \mapsto w_t^{b_2}$. Let $b_2^{*,upper} = \max \{ b_2^{*,u,upper}, b_2^{*,w,upper}\}$ and $M = \max \{  D^{u,b_2 \to \infty}+1, D^w+1\}$, we get a uniform upper bound for $u_t^{b_2}$ and $w_t^{b_2}$ for all $b_2\geq b_2^{*,upper}$, namely
	\begin{equation}
	\sup_{b_2 \geq b_2^{*,upper}} \sup_{0 \leq t \leq T} \max \left\{ u_t^{b_2} , w_t^{b_2}\right\} \leq M.
	\label{eq:ut_wt_upper_bound_b2_infty}
	\end{equation}

>>>>

	% lower bound for (b_2 + b2 bar) u_t
	Next, we derive a uniform lower bound for $(b_2 + \bar{b}_2) u_t^{b_2}$ over $[0,T]$ and large $b_2$. Let $\epsilon_1 > 0$ so that $\epsilon_1 < \min \left\{ c_{\delta_u^{b_2 \to \infty}}, D^{u,b_2 \to \infty} \right\}$. Then there exists $b_2^{*,lower} := b_2^{*,lower}(\epsilon_1) 	>0$ such that for all $b_2 \geq b_2^{*,lower}$,
	$$ 
	\max \left\{  \left\vert \frac{\delta_u^{+,b_2}}{b_2 + \bar{b}_2}  - c_{\delta_u^{b_2 \to \infty}} \right\vert, \   \left\vert \frac{\delta_u^{-,b_2}}{b_2 + \bar{b}_2}  - \left(-c_{\delta_u^{b_2 \to \infty}}\right) \right\vert, \vert D^{u,b_2} - D^{u,b_2\to \infty} \vert,  \left\vert \frac{1}{b_2 + \bar{b}_2} \right\vert  \right\} \leq \epsilon_1,
	$$ 
	and thus,
	\begin{IEEEeqnarray}{rCl}
		(b_2 + \bar{b}_2) u_t^{b_2} &\geq&  (b_2 + \bar{b}_2) \frac{D^{u,b_2} \delta_u^{+, b_2} }{ (\delta_u^{+,b_2} - \delta_u^{-,b_2}) + B^{b_2}D^{u,b_2} } \nonumber \\
		&=& \frac{D^{u,b_2} \frac{\delta_u^{+, b_2}}{b_2+ \bar{b}_2} }{ \frac{1}{b_2 + \bar{b}_2} \cdot \frac{\delta_u^{+,b_2} - \delta_u^{-,b_2}}{b_2 + \bar{b}_2} + \frac{D^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} } \nonumber \\
		&\geq& \frac{(D^{u,b_2 \to \infty} - \epsilon_1 ) \cdot (c_{\delta_u^{b_2 \to \infty}} - \epsilon_1) }{ \epsilon_1 \cdot (2 c_{\delta_u^{b_2 \to \infty}} + 2 \epsilon_1) + (D^{u,b_2 \to \infty} + \epsilon_1) / (r+ \bar{r}(1-\bar{s})^2) } =: m_u(\epsilon_1)
	\label{eq:ut_uniform_lower_bound_b2_infinity}
	\end{IEEEeqnarray}

	% upper bound for u_t, w_t
	Also, from equation (\ref{eq:riccati_ut_sol}), for any fixed $b_2$, we can compute the derivative of $u_t^{b_2}$ with respect to time $t$:
	\begin{equation*}
		\frac{d u_t^{b_2}}{dt} = \frac{\left(B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} \right) \cdot \left(\delta_u^{+,b_2} - \delta_u^{-,b_2}\right)^2 e^{- (\delta_u^{+,b_2} - \delta_u^{-,b_2})(T-t) } }{\left[B^{b_2} D^{u,b_2}(1-e^{- (\delta_u^{+,b_2} - \delta_u^{-,b_2})(T-t)})   + \delta_u^{+,b_2}e^{- (\delta_u^{+,b_2} - \delta_u^{-,b_2})(T-t)}- \delta_u^{-,b_2}  \right]^2 }.
	\end{equation*}
	Hence, the function $t \mapsto u_t^{b_2}$ is increasing if $B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} > 0$. Since 
	$$ B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} \xrightarrow[b_2 \to \infty]{} \infty,$$
	there exists $b_2^{*,u,upper}>0$ such that for all $b_2 \geq b_2^{*,u,upper}$, we have $t \mapsto u_t^{b_2}$ is increasing and 
	$$ \sup_{b_2 \geq b_2^{*,u,upper}} \sup_{0\leq t \leq T} \left\{ u_t^{b_2} \right\} = \sup_{b_2 \geq b_2^{*,u,upper}} \left\{ u_T^{b_2}\right\}  = \sup_{b_2 \geq b_2^{*,u,upper}} \{ D^{u,b_2}  \} \leq D^{u,b_2 \to \infty} + 1.$$ (ToDo: why 1 and not $\epsilon_1$?)
	Idem for $t \mapsto w_t^{b_2}$. Let $b_2^{*,upper} = \max \{ b_2^{*,u,upper}, b_2^{*,w,upper}\}$ and $M = \max \{  D^{u,b_2 \to \infty}+1, D^w\}$. Then for $b_2\geq b_2^{*,upper}$, we have the uniform upper bound:
	\begin{equation}
	\sup_{b_2 \geq b_2^{*,upper}} \sup_{0 \leq t \leq T} \max \left\{ u_t^{b_2} , w_t^{b_2}\right\} \leq M.
	\label{eq:ut_wt_upper_bound_b2_infty}
	\end{equation}
	(ToDo: why should we write the uniform upper bounds together? We can give them individually.)
